Comments on Latent Ranking

### 2020-09-03 output_scripts/aug_updates.Rmd
update prepare data to allow for permutation. change permute function to take data rather than cohort.

```{r shuffle cohort and stan fit, slow locally}
current_cohort <- 8

print(paste("Cohort",current_cohort))
###
stan_input_lst <- prepareData_permute_Stan(current_cohort)
### get the corresponding expert rank
permuted_data <- stan_input_lst$permuted_data

@@

@@

>>>>

```{r permute the raw data, include=FALSE, eval=FALSE}
# first want to check if permuting the raw data is doing what it should
current_cohort <- 1

orig_data <- full_data[[cohort_names[current_cohort]]]
perm_data <- permute_raw(orig_raw = orig_data)

dim(orig_data)
dim(perm_data)
summary(orig_data$Actor)
summary(perm_data$Actor)
## these look more regular, all equally likely to be an actor. good so far

## then clean these and compare
orig_clean <- cleanData(raw_data = orig_data,cut_off = 1)
perm_clean <- cleanData(raw_data = perm_data,cut_off = 1)

sum(orig_clean$N_count)
sum(perm_clean$N_count)
## how do these differ?, should both have 1077. unless identical times and mice?
## rows 107,108 have same mice fighting different at identical time. that would cause it?
## then cleanObservation Period on each of these
orig_period <- cleanObservationPeriod(current_cohort = 1, raw_df = orig_data,
                                      clean_data = orig_clean)
perm_period <- cleanObservationPeriod(current_cohort = 1,raw_df = perm_data,
                                      clean_data = perm_clean)

sum(orig_period$no.events) # surely this should match with above?
sum(perm_period$no.events)

## these seem ok anyway
```

```{r further checking permutation}
orig_stan_data <- prepareDataStan(current_cohort = 1)
permute_stan_data <- prepareData_permute_Stan(current_cohort = 1)
# now all pairs have an interaction

```{r shuffle cohort and stan fit, slow locally, include=FALSE,eval=FALSE}
source(paste(func_dir,'permute_data.R',sep = ""))

current_cohort <- 1

print(paste("Cohort",current_cohort))
###
stan_input_lst <- prepareDataStan(current_cohort)
stan_input_lst_permute <- prepareData_permute_Stan(current_cohort)
### get the corresponding expert rank
permuted_data <- stan_input_lst_permute$permuted_data

@@

sum(stan_input_lst$Nm - stan_input_lst_permute$Nm) 
# these should be the same size surely?

# seems these are identical... good!

@@

```{r}
real_cleaned <- cleanData(full_data[[cohort_names[current_cohort]]])

permuted <- permute_raw(current_cohort)
permuted_cleaned <- cleanData(permuted)

permuted_cleaned$N_count - real_cleaned$N_count
# these look different which is good

return_df <- cleanObservationPeriod(current_cohort,
                                    full_data[[cohort_names[current_cohort]]],
                                    real_cleaned)

per_return_df <- cleanObservationPeriod(current_cohort,permuted,permuted_cleaned)

return_df$initiator - per_return_df$initiator
# so this is the issue then possibly

```{r compare fits from permuted and true data}
current_cohort <- 4

## load true model fit
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

true_fit <- fit_cohort_mmhp
true_post <- sim_cohort_mmhp

## load permuted model fit
load(paste(data_path,cohort_names[current_cohort],
           "/permute_cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

perm_fit <- fit_cohort_mmhp
perm_post <- sim_cohort_mmhp

mice_covars <- tibble(true_rank = apply(true_post$f,2,mean),
       perm_rank = apply(perm_post$f,2,mean),
       true_gam = apply(true_post$gamma,2,mean),
       perm_gam = apply(perm_post$gamma,2,mean),
       true_zeta = apply(true_post$zeta,2,mean),
       perm_zeta = apply(perm_post$zeta,2,mean))

mice_covars %>% ggplot(aes(true_rank,perm_rank)) + geom_point()

mice_covars %>% ggplot(aes(true_gam,perm_gam)) + geom_point()

mice_covars %>% ggplot(aes(true_zeta,perm_zeta)) + geom_point()
